\bf Supplementary Material: What is the Best Way to Display Two Time Series to Read Association?

### 2016-01-27 paper/supplementary.Rnw
supplementary

@@

\begin{figure}[htbp]
\centering
<<users, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
users <- read.csv("turk18_users.csv")
users$gender <- ifelse(users$gender==1, "Male", "Female")
ggplot(data=users, aes(x=factor(age), fill=factor(academic_study))) + geom_bar() + facet_wrap(~gender) +
  scale_fill_manual(values=c("#550000", "#883388", "#1133FF", "#FF9933", "#555555"))
@
\caption{Age and education by gender. Most subjects are in the younger brackets and there are more males than females}
\label{ageed}
\end{figure}

@@

\begin{figure}[htbp]
\centering
<<choices, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
full$choice_reason <-sapply(strsplit(as.character(unlist(full$choice_reason)), "[^0-9]+"), "[[", 1)
choice <- full %>% transform(choice_reason= strsplit(as.character(choice_reason), "")) %>% unnest(choice_reason)
choice$rsgn <- factor(choice$rsgn, labels=c("r -","r +"))
choice$correct <- factor(choice$correct, labels=c("Did not detect", "Detected"))
ggplot(data=choice, aes(x=choice_reason, fill=correct)) + geom_bar() + facet_grid(design~rsgn) +
  theme(legend.position="bottom", axis.title=element_blank()) + scale_fill_discrete(name="True Plot")
@
\caption{Reasons given for plot selection}
\label{reasons}
\end{figure}

\begin{figure}[htbp]
\centering 
<<avscore, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>= 
subjplot <- summarise(group_by(full.sub, subj_id), eval=sum(weights), total = sum(score))
subjplot <- mutate(subjplot, avscore= total/eval)
ggplot(data=subjplot, aes(x=avscore)) + geom_histogram(binwidth=0.05)
@
\caption{Average score of subjects included in modelling}
\label{avscore}
\end{figure}

\begin{figure}[htbp]
\centering
<<multiselect, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
m.select <- summarise(group_by(subset(full.sub, attempts>1), subj_id, pic_id), attempts=max(attempts))
m.freq <- data.frame(table(m.select$pic_id))
m.lineup <- merge(m.freq, bylineup, by.x="Var1", by.y="pic_id")
ggplot(data=m.lineup) + geom_bar(aes(x=factor(r), fill=design), binwidth=0.2) + facet_grid(n~smoothed) + labs(y="Count", x="True plot correlation")
@
\caption{Characteristics of lineups with at least one subject making multiple selections}
\label{lineupmulti}
\end{figure}

\begin{table}[htbp]
\caption{Number of selections per lineup evaluation. The subject with the most selections is reported.}
\label{table}
<<tabattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
attempts <- summarise(group_by(full.sub, subj_id, pic_id), attempts = max(attempts))
attempts.table <- data.frame(table(attempts$attempts))
attempts.table$most <- c(0,0,0,5,3,1,1)
colnames(attempts.table) <- c("Selections", "Whole Sample", "Subject 123")
kable(attempts.table, format="latex")
@
\end{table}

\begin{figure}[htbp]
\centering
<<multiattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
ggplot(data=attempts) + geom_bar(aes(x=as.factor(attempts))) + labs(x="Number of selections", y=NULL)
@
\caption{Histogram of table~\ref{table}}
\label{attemptshist}
\end{figure}

@@

Analysing the level one residuals, $\hat{\epsilon_{i}}$, and level two residuals, $\hat{\gamma_{i}}$, allows us to test the model fit as described \citet{Loy}. There are some negative extreme outliers but the distributional assumption appears to hold.

@@

The scores of each subject given by equation 5 of the main paper can be summed to give a total score per subject $j$:

>>>>

\section{Lineup Results}

@@

\begin{figure}[htbp]
\centering
<<users, dependson='setup', echo=FALSE, results='asis', fig.height=3, message=FALSE, error=FALSE, warning=FALSE>>=
users <- read.csv("turk18_users.csv")
users$academic_study <- factor(users$academic_study)
levels(users$academic_study) <- c("At Most High School", "Some Undergraduate", "Undergraduate Degree", "Some Postgraduate", "Postgraduate Degree")
users$age <- factor(users$age)
levels(users$age) <- c("18-25", "26-30", "31-35", "36-40", "41-45", "46-50", "51-55", "56-60", "61+")
ggplot(data=users, aes(x=age, fill=academic_study)) + geom_bar() + facet_wrap(~gender) +
  scale_fill_manual(name = element_blank(), values=c("#550000", "#883388", "#1133FF", "#FF9933", "#555555")) + labs(x="Age", y=element_blank()) + theme(axis.text.x = element_text(angle = 270))
@
\caption{Age and education by gender. Most subjects are in the younger brackets and there are more males than females}
\label{ageed}
\end{figure}

This section describes the demographics of the subjects in the experiment recruited through Amazon's Mechanical Turk. Age, gender, education and location all did not have a statistically significant effect on the selections made.

@@

\begin{figure}[h]
\centering
<<choices, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
full$choice_reason <-sapply(strsplit(as.character(unlist(full$choice_reason)), "[^0-9]+"), "[[", 1)
choice <- full %>% transform(choice_reason= strsplit(as.character(choice_reason), "")) %>% unnest(choice_reason)
choice$rsgn <- factor(choice$rsgn, labels=c("r -","r +"))
choice$correct <- factor(choice$correct, labels=c("Did not detect", "Detected"))
choice$choice_reason <- factor(choice$choice_reason)
levels(choice$choice_reason) <- c("Close Together", "Matching Peaks", "Pattern Formed", "Formed a line", "Other")
ggplot(data=choice, aes(x=choice_reason, fill=correct)) + geom_bar() + facet_grid(design~rsgn) +
  theme(legend.position="bottom", axis.title=element_blank()) + scale_fill_discrete(name="True Plot")
@
\caption{Reasons given for plot selection. After controlling for lineup factors, any explanatory power of the reason is removed.}
\label{reasons}
\end{figure}

\begin{figure}[htbp]
\centering
<<multiselect, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
m.select <- summarise(group_by(subset(full.sub, attempts>1), subj_id, pic_id), attempts=max(attempts))
m.freq <- data.frame(table(m.select$pic_id))
m.lineup <- merge(m.freq, bylineup, by.x="Var1", by.y="pic_id")
ggplot(data=m.lineup) + geom_bar(aes(x=factor(r), fill=design)) + facet_grid(n~smoothed) + labs(y="Count", x="True plot correlation")
@
\caption{Characteristics of lineups with at least one subject making multiple selections. Overlaid lines lineups have multiple selections more often, and true plot correlation does not appear to have an impact except at large sample sizes.}
\label{lineupmulti}
\end{figure}

\begin{table}[h]
\caption{Number of selections for each lineup evaluation. The subject with the most selections is additionally reported.}
\label{table}
<<tabattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
attempts <- summarise(group_by(full.sub, subj_id, pic_id), attempts = max(attempts))
attempts.table <- data.frame(table(attempts$attempts))
attempts.table$most <- c(0,0,0,5,3,1,1)
colnames(attempts.table) <- c("Selections", "Whole Sample", "Subject 123")
kable(attempts.table, format="latex")
@
\end{table}

\iffalse
\begin{figure}[htbp]
\centering
<<multiattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
ggplot(data=attempts) + geom_bar(aes(x=as.factor(attempts))) + labs(x="Number of selections", y=NULL)
@
\caption{Histogram of table~\ref{table}}
\label{attemptshist}
\end{figure}
\fi

Subjects are allowed to make multiple selections on each lineup evaluation, with a score for each evaluation defined by:

\begin{equation}
\label{score}
{score}_{ij} =\frac{m-s_{ij}}{m-1} \mathbbm{I}_{ij}
\end{equation}

Where $m = 20$, the number of plots in a linup, $s_{ij}$ is the number of selections made by subject $i$ on lineup $j$ and $\mathbbm{I}_{ij} = 1$ if the true plot is detected, $0$ otherwise. The most selections made on any lineup evaluation is 8.

\begin{figure}[htbp]
\centering 
<<avscore, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>= 
subjplot <- summarise(group_by(full.sub, subj_id), eval=sum(weights), total = sum(score))
subjplot <- mutate(subjplot, avscore= total/eval)
ggplot(data=subjplot, aes(x=avscore)) + geom_histogram(binwidth=0.1)
@
\caption{The average score of our subjects, according to formula \ref{score}. There is a wide range of visual ability to be controlled with random effects in the modelling}
\label{avscore}
\end{figure}

@@

Analysing the level one residuals, $\hat{\epsilon_{i}}$, and level two residuals, $\hat{\gamma_{i}}$, allows us to test the model fit as described \citet{Loy}. There are some negative extreme outliers but the distributional assumptions appear to hold.

@@

The scores of each subject given by equation~\ref{score} be summed to give a total score per subject $j$:
